Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-02 doc/sc2012/soop.tex
distribution subsection

>>>>

Once task $t$'s dependences have been analyzed, the distribution phase
determines on which processor $t$ will run.  Subsequently the
mapping phase chooses the physical instances of its logical
regions that $t$ will use.  However, in choosing the processor and
physical instances for $t$, it is helpful to know the processors and
physical instances used by the tasks $t$ depends on---and not just for
performance, but for correctness.  Thus, the first step in
distribution is that $t$ waits for all tasks on which $t$ depends to
map; nothing happens to $t$ during this time.  Once $t$'s mapping
dependences are satisfied, $t$ is ready to be mapped and places
itself in the mapping queue.

Once in the mapping queue, SOOPs on other processors in the system may
ask to steal $t$ from its home SOOP.  The home SOOP may decline the
request, but if the request is granted, task $t$ along with a copy of
$t$'s region forest is sent to the remote SOOP.  If $t$ has not been
stolen when it reaches the head of the queue, the SOOP decides whether
to execute $t$ on the local processor or send it to another processor.

Thus, task distribution to processors in Legion is both ``pull'' (stealing) and ``push''.
The various policies (whether steal requests are granted, when to send
a task to another processor and which processor to send it to, and when to
try to steal tasks from other SOOPs) are part of the {\em mapping interface}
and can be defined by the user (see Section~\ref{sec:mapping}).
